\chapter*{Literaturverzeichnis}
\addcontentsline{toc}{chapter}{Literaturverzeichnis}

\begin{sloppy}
\begin{verse}
{\bf Aldenderfer, M.S., Blashfield, R.K. [1984]:} Cluster Analysis,
	Series: Quantitative Applicatons in the Social Sciences, 
	Sage Publications, Newbury Park.

{\bf Anderberg, M.R. [1973]:} Cluster Analysis for Applications, 
	Academic Press.

{\bf Blazewicz, J., Ecker, K., Schmidt, G., Weglarz, J. [1992]:}
	Sche\-du\-ling in Computer and Manufacturing Systems, Springer, Berlin.

{\bf Bock, H.H. [1974]:} Automatische Klassifikation, Vandenhoeck \& 
	Rup\-recht, G"ot\-tin\-gen.

{\bf Brucker, P. [1995]:} Scheduling Algorithms, Springer, Berlin.

{\bf Brucker, P., Hurink, J., Werner, F. [1993]:} Improving local search
	heuristics for some scheduling problems I, to appear in:
	Discrete Applied Mathematics.

{\bf Brucker, P. [1978]:} On the complexity of clustering problems,
	Optimierung und Operations Research, Lecture Notes in
	Economics and Mathematical Systems, Springer, Berlin.

{\bf Day, W., Edelsbrunner, H. [1984]:} Efficient Algorithms for
	Agglomerative Hie\-rar\-chi\-cal Clustering Methods, Journal of
	Classification, 7--24.

{\bf Duran, B.S., Odell, P.L. [1974]:} Cluster Analysis A Survey, 
	Lecture Notes in Economical Mathematical Systems, Springer, Berlin.

{\bf Edelsbrunner, H. [1987]:} Algorithms in Combinatorial Geometry,
	Springer.

{\bf Garey, M.R., Johnson, D.S. [1979]:} Computer and Intractability:
	A Guide to the Theory of NP--Completeness, Freeman, San Francisco.

{\bf Godehardt, E. [1990]:} Graphs as Structural Models, Advances
	in System Analysis, Volume 4, Vieweg, Braunschweig.

{\bf Gordon, A.D. [1980]:} Classification, Chapman and Hall, London,
	New York.

{\bf Hajek, B. [1988]:} Cooling Schedules for optimal annealing, 
	Math. Oper. Res. 13, 311--329.

{\bf Jacobs, K. [1983]:} Einf"uhrung in die Kombinatorik, Walter de
	Gruyter, Berlin, New York.

{\bf Jensen, R.E. [1969]:} A Dynamic Programming Algorithm for Cluster
	Analysis, Operations Research 12, 1034--57.

{\bf Laarhoven, P.J.M van [1988]:} Theoretical and computational
	aspects of simulated annealing, CWI 51.

{\bf Laarhoven, P.J.M. van, Aarts, E.H.L. [1987]:} Simu\-lated Annea\-ling:
	Theo\-ry and Ap\-pli\-ca\-tions, D. Reidel Publishing Company, Dordrecht,
	Holland.

{\bf Lades, R. [1976]:} CLAN; ein EDV--Programm zur Clusteranalyse
	f"ur die Rechneranlage CD 3300, Arbeitspapiere /
	Betriebswirtschaftliches Institut N"urnberg, 26.

{\bf L"uneburg, H. [1971]:} Kombinatorik, Birkh"auser Verlag, Basel
	und Stuttgart.

{\bf Mahanalobis, P.C. [1936]:} On the generalized distance in statistics,
	Proc. Nat. Inst. Sci. India 2, 49--55.

{\bf Milligan, G.W., Cooper, M.C. [1988]:} A Study of Standardization of
	Variables in Cluster Analysis, Journal of Classification 5, 181--204.

{\bf Papadimitriou, C.H., Steiglitz, K. [1982]:} Combinatorial 
	Optimization: Algorithms and Complexity, Prentice Hall, New York.

{\bf Preparata, F.P., Shamos, M.I. [1985]:} Computational
	Geometry --- An Introduction, Springer.

{\bf Rao, M.R. [1971]:} Cluster Analysis and Mathematical Programming,
	Journal of the American Statistical Association 66.

{\bf Sp"ath, H. [1980]:} Cluster--Analyse--Algorithmen zur
	Objektklassifizierung und Datenreduktion, R. Oldenbourg Verlag,
	M"unchen, Wien.

{\bf Steinhausen, D., Langer, K. [1977]:} Clusteranalyse, Walter de
	Gruyter, Berlin, New York.

{\bf Stockmeyer, L. [1973]:} Planar 3--colorability is Polynomial
	Complete, ACM Sigact News 5, 3, 19--25.

\end{verse}
\end{sloppy}
